Equations & R Code

### 2017-03-07 manuscript/coexistence-stability_SI.Rmd
exploring parameter space writing

Conditions 1 \& 2 are already included in our main analysis because we present results across a spectrum of correlations among species' environmental responses (condition 1) and across gradients of environmental variation (condition 2).
Here, we show how the patterns described in the main text change as the buffering of populaion growth declines (condition 3).
We do this by conducting the same simulations as in Figure 3 of the main text, but for one set of live-to-dormant transition rates ($\alpha$s) and with two levels (high and low) of dormant mortality rates ($\eta$s).
Our results are qualitatively similar: (1) increasing environmental variation allows more species to coexist, creating a positive relationship between species richness and ecosystem variability; (2) and at any given level of environmental variability, it is always better to have more species, creating a within-site negative relationship between species richness and ecosystem variability.
However, the rate at which species richness buffers ecosystem variability declines as dormant mortality increases (compare curves of each color among top and bottom panels).

@@

*CV* scaled by the mean, and we don't have demographic stochasticity because we are assuming large populations, so reducing overall competition to get over-yielding doesn't matter here.

>>>>

Conditions 1 \& 2 are already included in our main analysis because we present results across a spectrum of correlations among species' environmental responses (condition 1) and across gradients of environmental variation (condition 2).
Here, we show how the patterns described in the main text change as the buffering of populaion growth declines (condition 3).
We do this by conducting the same simulations as in Figure 3 of the main text, but for one set of live-to-dormant transition rates ($\alpha$s) and with two levels (high and low) of dormant mortality rates ($\eta$s).

Our results are qualitatively similar: (1) increasing environmental variation allows more species to coexist, creating a positive relationship between species richness and ecosystem variability; (2) and at any given level of environmental variability, it is always better to have more species, creating a within-site negative relationship between species richness and ecosystem variability (Fig. S1-1).
Although the qualitative patterns are similar, increasing the dormant mortality rate has two interesting effects: (1) it makes coexistence more difficult, (2) it reduces the absolute value of ecosystem *CV* by reducing mean population size a little bit and by reducing the temporal standard deviation a lot, and (3) it weakens the buffering effect of additional species (compare the spread of the lines between top and bottom panels of Fig. S1-1).
The second result occurs because population fluctuations are reduced when very little biomass can be activated to the live stage at the beginning of each season.
That is, in terms of an annual plant, germination of live biomass is always a fraction of a very small number.
The third result is a consequence of the second: populations are not fluctuating that much, so total *CV* can only be reduced by so much with the addition of another species.

@@

*CV* scaled by the mean, and we don't have demographic stochasticity because we are assuming large populations, so reducing overall competition to get over-yielding doesn't matter here...

### 2017-03-07 manuscript/coexistence-stability_SI.tex
changes font size to 11
exploring parameter space writing

\documentclass[12pt,]{article}

@@

Conditions 1 \& 2 are already included in our main analysis because we
present results across a spectrum of correlations among species'
environmental responses (condition 1) and across gradients of
environmental variation (condition 2). Here, we show how the patterns
described in the main text change as the buffering of populaion growth
declines (condition 3). We do this by conducting the same simulations as
in Figure 3 of the main text, but for one set of live-to-dormant
transition rates (\(\alpha\)s) and with two levels (high and low) of
dormant mortality rates (\(\eta\)s). Our results are qualitatively
similar: (1) increasing environmental variation allows more species to
coexist, creating a positive relationship between species richness and
ecosystem variability; (2) and at any given level of environmental
variability, it is always better to have more species, creating a
within-site negative relationship between species richness and ecosystem
variability. However, the rate at which species richness buffers
ecosystem variability declines as dormant mortality increases (compare
curves of each color among top and bottom panels).

@@

\emph{CV} scaled by the mean, and we don't have demographic
stochasticity because we are assuming large populations, so reducing
overall competition to get over-yielding doesn't matter here.

>>>>

\documentclass[11pt,]{article}

@@

Conditions 1 \& 2 are already included in our main analysis because we
present results across a spectrum of correlations among species'
environmental responses (condition 1) and across gradients of
environmental variation (condition 2). Here, we show how the patterns
described in the main text change as the buffering of populaion growth
declines (condition 3). We do this by conducting the same simulations as
in Figure 3 of the main text, but for one set of live-to-dormant
transition rates (\(\alpha\)s) and with two levels (high and low) of
dormant mortality rates (\(\eta\)s).

Our results are qualitatively similar: (1) increasing environmental
variation allows more species to coexist, creating a positive
relationship between species richness and ecosystem variability; (2) and
at any given level of environmental variability, it is always better to
have more species, creating a within-site negative relationship between
species richness and ecosystem variability (Fig. S1-1). Although the
qualitative patterns are similar, increasing the dormant mortality rate
has two interesting effects: (1) it makes coexistence more difficult,
(2) it reduces the absolute value of ecosystem \emph{CV} by reducing
mean population size a little bit and by reducing the temporal standard
deviation a lot, and (3) it weakens the buffering effect of additional
species (compare the spread of the lines between top and bottom panels
of Fig. S1-1). The second result occurs because population fluctuations
are reduced when very little biomass can be activated to the live stage
at the beginning of each season. That is, in terms of an annual plant,
germination of live biomass is always a fraction of a very small number.
The third result is a consequence of the second: populations are not
fluctuating that much, so total \emph{CV} can only be reduced by so much
with the addition of another species.

@@

\emph{CV} scaled by the mean, and we don't have demographic
stochasticity because we are assuming large populations, so reducing
overall competition to get over-yielding doesn't matter here\ldots{}
